---
title: "Descriptive Stats"
#author: "Sarah"
#date: "December 11, 2015"
output: html_document
css: style.css
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r descriptions, echo=FALSE, eval=TRUE, include=FALSE}
options(width=120)
filepath = "/home/sarah/rprojects/vars/"
load(paste(filepath, "DATA", sep="/"))
str(DATA)
library(psych)
soundidx_withsound <- which(DATA$sound == 0)
soundidx_nosound <- which(DATA$sound == -99999) 
fadingidx_800 <- which(DATA$fading_function == 800)
fadingidx_0 <- which(DATA$fading_function == 0)
fadingidx_nolight <- which(DATA$fading_function == -1)
angleidx_nolight <- which(DATA$LEDangle == -1)
angleidx_rightside <- which(DATA$LEDangle == 45)
angleidx_leftside <- which(DATA$LEDangle == -45)
angleidx_central <- which(DATA$LEDangle == 0)

```

# Reaction Time Primary Task
## No Sound
```{r output1, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_nosound, ]$reactionTime_PT) #reaction_time_ST, correct
describe(DATA[soundidx_nosound, ]$reactionTime_PT) #reaction_time_ST, correct
```

## With Sound
```{r output 2, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_withsound, ]$reactionTime_PT) #reaction_time_ST correct)
describe(DATA[soundidx_withsound, ]$reactionTime_PT) #reaction_time_ST correct)
```

## No Light
```{r output3, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_nolight, ]$reactionTime_PT)
describe(DATA[fadingidx_nolight, ]$reactionTime_PT)
```

## No Fading
```{r output4, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_0, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[fadingidx_0, ]$reactionTime_PT) 
```

## Fading = 800
```{r output5, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_800, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[fadingidx_800, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED left
```{r output6, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_leftside, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_leftside, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED right
```{r output7, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_rightside, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_rightside, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED central
```{r output7.5, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_central, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_central, ]$reactionTime_PT) #reaction_time_ST correct
```

# Reaction Time Secondary Task
## No Sound
```{r output8, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_nosound, ]$reaction_time_ST) #reaction_time_ST, correct
describe(DATA[soundidx_nosound, ]$reaction_time_ST) #reaction_time_ST, correct
```

## With Sound
```{r output 9, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_withsound, ]$reaction_time_ST) #reaction_time_ST correct)
describe(DATA[soundidx_withsound, ]$reaction_time_ST) #reaction_time_ST correct)
```

## No Light
```{r output10, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_nolight, ]$reaction_time_ST)
describe(DATA[fadingidx_nolight, ]$reaction_time_ST)
```

## No Fading
```{r output11, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_0, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[fadingidx_0, ]$reaction_time_ST) 
```

## Fading = 800
```{r output12, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_800, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[fadingidx_800, ]$reaction_time_ST) #reaction_time_ST correct
```

## LED left
```{r output13, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_leftside, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[angleidx_leftside, ]$reaction_time_ST) #reaction_time_ST correct
```

## LED right
```{r output14, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_rightside, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[angleidx_rightside, ]$reaction_time_ST) #reaction_time_ST correct
```

# Combined RT PT

## Angle left, fading = 0, no sound
```{r output15, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
```

## Angle left, fading = 800, no sound
```{r output16, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output17, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output19, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
```

## Angle right, fading = 800, no sound
```{r output20, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output21, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```


## No Light, no sound
```{r output23, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## No light with sound
```{r output24, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output25, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output26, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```


# RT ST

## Angle left, fading = 0, no sound
```{r output28, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
```

## Angle left, fading = 800, no sound
```{r output29, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output30, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output31, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
```

## Angle right, fading = 800, no sound
```{r output32, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output33, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```


## No Light, no sound
```{r output34, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## No light with sound
```{r output35, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output36, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output37, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

# Correct

## Angle left, fading = 0, no sound
```{r output38, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$correct)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$correct)
```

## Angle left, fading = 800, no sound
```{r output39, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output40, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output41, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$correct)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$correct)
```

## Angle right, fading = 800, no sound
```{r output42, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output43, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
```


## No Light, no sound
```{r output44, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## No light with sound
```{r output45, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$correct) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output46, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output47, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

```{r misc, echo=TRUE, include=TRUE, eval=FALSE}
load(paste(filepath, "results", sep="/"))
angleidx_peripher <- union(angleidx_leftside, angleidx_rightside) # for friedman
fading_factor <- factor(DATA$fading_function) 

## Change the shit
# angle = left
rtPTleft_fading0_nosound <- DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTleft_fading800_nosound <- DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct

rtPTleft_fading0_withsound <- DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT #reaction_time_ST correct

# angle = right
rtPTright_fading0_nosound <- DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTright_fading800_nosound <- DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct

rtPTright_fading0_withsound <- DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT #reaction_time_ST correct

# angle = no light
rtPTonly_nosound <- DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct

rtPTonly_withsound <- DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reactionTime_PT #reaction_time_ST correct

# angle = central
rtPTcentral_fading0_nosound <- DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTcentral_fading800_nosound <- DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct

rtPTcentral_fading0_withsound <- DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_withsound), ]$reactionTime_PT #reaction_time_ST correct

## for Friedman I also need angle = peripher as a combined group 
rtPTperipher_fading800_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_800), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTperipher_fading0_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTperipher_fading0_withsound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_withsound), ]$reactionTime_PT #reaction_time_ST correct


#######
##
## Ranked ANOVA
## 
library(lme4)
rankedPT <- rank(DATA$reactionTime_PT)
ranked_priming_model <- lmer(rankedPT ~ fading_factor + (1|DATA$trialnumber) + (1 + fading_factor|DATA$subject), data = DATA)
results$rankedAnova <- anova(ranked_priming_model)

describe(results$rankedAnova)

summary(aov(rankedPT ~ fading_factor + angle_factor + sound_factor))
```
