---
title: "Descriptive Stats"
#author: "Sarah"
#date: "December 11, 2015"
output: html_document
css: style.css
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r descriptions, echo=FALSE, eval=TRUE, include=FALSE}
setwd("~/Master/WS15-16/HiwiJobAndreas/rprojects")
filepath = "./vars/"
load(paste(filepath, "DATA", sep="/"))
str(DATA)
library(psych)
soundidx_withsound <- which(DATA$sound == 0)
soundidx_nosound <- which(DATA$sound == -99999) 
fadingidx_800 <- which(DATA$fading_function == 800)
fadingidx_0 <- which(DATA$fading_function == 0)
fadingidx_nolight <- which(DATA$fading_function == -1)
angleidx_nolight <- which(DATA$LEDangle == -1)
angleidx_rightside <- which(DATA$LEDangle == 45)
angleidx_leftside <- which(DATA$LEDangle == -45)
angleidx_central <- which(DATA$LEDangle == 0)

rtPT <- DATA$reactionTime_PT
rtST <- DATA$reaction_time_ST
corr <- DATA$correct

fading_factor <- factor(DATA$fading_function) 
angle_factor <- factor (DATA$LEDangle)
levels(angle_factor) <- c("periphery", "no_light", "central", "periphery")
# angle is only looked at with two possibilities IF light was presented: central and periphery
sound_factor <- factor(DATA$sound)
# subject must be a factor for a within subject anova
subject_factor <- factor(DATA$subject)

```

# Reaction Time Primary Task
## No Sound
```{r output1, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_nosound, ]$reactionTime_PT) #reaction_time_ST, correct
describe(DATA[soundidx_nosound, ]$reactionTime_PT) #reaction_time_ST, correct
```

## With Sound
```{r output 2, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_withsound, ]$reactionTime_PT) #reaction_time_ST correct)
describe(DATA[soundidx_withsound, ]$reactionTime_PT) #reaction_time_ST correct)
```

## No Light
```{r output3, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_nolight, ]$reactionTime_PT)
describe(DATA[fadingidx_nolight, ]$reactionTime_PT)
```

## No Fading
```{r output4, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_0, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[fadingidx_0, ]$reactionTime_PT) 
```

## Fading = 800
```{r output5, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_800, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[fadingidx_800, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED left
```{r output6, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_leftside, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_leftside, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED right
```{r output7, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_rightside, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_rightside, ]$reactionTime_PT) #reaction_time_ST correct
```

## LED central
```{r output7.5, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_central, ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[angleidx_central, ]$reactionTime_PT) #reaction_time_ST correct
```

# Reaction Time Secondary Task
## No Sound
```{r output8, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_nosound, ]$reaction_time_ST) #reaction_time_ST, correct
describe(DATA[soundidx_nosound, ]$reaction_time_ST) #reaction_time_ST, correct
```

## With Sound
```{r output 9, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_withsound, ]$reaction_time_ST) #reaction_time_ST correct)
describe(DATA[soundidx_withsound, ]$reaction_time_ST) #reaction_time_ST correct)
```

## No Light
```{r output10, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_nolight, ]$reaction_time_ST)
describe(DATA[fadingidx_nolight, ]$reaction_time_ST)
```

## No Fading
```{r output11, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_0, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[fadingidx_0, ]$reaction_time_ST) 
```

## Fading = 800
```{r output12, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_800, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[fadingidx_800, ]$reaction_time_ST) #reaction_time_ST correct
```

## LED left
```{r output13, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_leftside, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[angleidx_leftside, ]$reaction_time_ST) #reaction_time_ST correct
```

## LED right
```{r output14, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_rightside, ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[angleidx_rightside, ]$reaction_time_ST) #reaction_time_ST correct
```

# Correct
## No Sound
```{r outputc8, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_nosound, ]$correct) #reaction_time_ST, correct
describe(DATA[soundidx_nosound, ]$correct) #reaction_time_ST, correct
```

## With Sound
```{r outputc9, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[soundidx_withsound, ]$correct) #reaction_time_ST correct)
describe(DATA[soundidx_withsound, ]$correct) #reaction_time_ST correct)
```

## No Light
```{r outputc10, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_nolight, ]$correct)
describe(DATA[fadingidx_nolight, ]$correct)
```

## No Fading
```{r outputc11, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_0, ]$correct) #reaction_time_ST correct
describe(DATA[fadingidx_0, ]$correct) 
```

## Fading = 800
```{r outputc12, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[fadingidx_800, ]$correct) #reaction_time_ST correct
describe(DATA[fadingidx_800, ]$correct) #reaction_time_ST correct
```

## LED left
```{r outputc13, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_leftside, ]$correct) #reaction_time_ST correct
describe(DATA[angleidx_leftside, ]$correct) #reaction_time_ST correct
```

## LED right
```{r outputc14, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[angleidx_rightside, ]$correct) #reaction_time_ST correct
describe(DATA[angleidx_rightside, ]$correct) #reaction_time_ST correct
````


# Combined RT PT

## Angle left, fading = 0, no sound
```{r output15, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
```

## Angle left, fading = 800, no sound
```{r output16, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output17, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output19, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reactionTime_PT)
```

## Angle right, fading = 800, no sound
```{r output20, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output21, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```


## No Light, no sound
```{r output23, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## No light with sound
```{r output24, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output25, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output26, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT) #reaction_time_ST correct
```
```{r periphe, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}

```

# RT ST

## Angle left, fading = 0, no sound
```{r output28, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
```

## Angle left, fading = 800, no sound
```{r output29, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output30, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output31, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$reaction_time_ST)
```

## Angle right, fading = 800, no sound
```{r output32, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output33, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```


## No Light, no sound
```{r output34, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## No light with sound
```{r output35, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output36, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output37, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reaction_time_ST) #reaction_time_ST correct
```

# Correct

## Angle left, fading = 0, no sound
```{r output38, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$correct)
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_nosound), ]$correct)
```

## Angle left, fading = 800, no sound
```{r output39, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Angle left, fading = 0, with sound
```{r output40, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_leftside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
```


## Angle right, fading = 0, no sound
```{r output41, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$correct)
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_nosound), ]$correct)
```

## Angle right, fading = 800, no sound
```{r output42, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Angle right, fading = 0, with sound
```{r output43, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_rightside, fadingidx_0), soundidx_withsound), ]$correct) #reaction_time_ST correct
```


## No Light, no sound
```{r output44, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## No light with sound
```{r output45, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_nolight, fadingidx_nolight), soundidx_withsound), ]$correct) #reaction_time_ST correct
```

## Central LED, fading = 0, no sound
```{r output46, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$correct) #reaction_time_ST correct
```

## Central LED, fading = 800, no sound
```{r output47, echo=FALSE, include=TRUE, eval=TRUE, collapse=TRUE}
summary(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
describe(DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$correct) #reaction_time_ST correct
```


## Combined peripher angle

```{r misc, echo=15:23, include=TRUE, eval=TRUE}
setwd("~/Master/WS15-16/HiwiJobAndreas/rprojects")
filepath = "./vars/"
load(paste(filepath, "results", sep="/"))
angleidx_peripher <- union(angleidx_leftside, angleidx_rightside) # for friedman
fading_factor <- factor(DATA$fading_function) 
rtPTperipher_fading800_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_800), soundidx_nosound), ]$reactionTime_PT #reaction_time_ST correct
rtPTperipher_fading0_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_nosound), ]$reactionTime_PT#eaction_time_ST correct
rtPTperipher_fading0_withsound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_withsound), ]$reactionTime_PT

rtSTperipher_fading800_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_800), soundidx_nosound), ]$reactionTime_ST #reaction_time_ST correct
rtSTperipher_fading0_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_nosound), ]$reactionTime_ST#eaction_time_ST correct
rtSTperipher_fading0_withsound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_withsound), ]$reactionTime_ST

correctperipher_fading800_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_800), soundidx_nosound), ]$correct #reaction_time_ST correct
correctperipher_fading0_nosound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_nosound), ]$correct#eaction_time_ST correct
correctperipher_fading0_withsound <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_withsound), ]$correct

summary(rtPTperipher_fading0_withsound)
summary(rtPTperipher_fading0_withsound)
summary(rtPTperipher_fading800_nosound)
summary(correctperipher_fading0_withsound)
summary(correctperipher_fading0_nosound)
summary(correctperipher_fading800_nosound)

#summary(rtSTperipher_fading0_withsound)
#summary(rtSTperipher_fading0_nosound)
#summary(rtSTperipher_fading800_nosound)

```


```{r rankedanova}

#######
##
## Ranked ANOVA
## 
library(lme4)
rankedPT <- rank(DATA$reactionTime_PT)
ranked_priming_model <- lmer(rankedPT ~ fading_factor + (1|DATA$trialnumber) + (1 + fading_factor|DATA$subject), data = DATA)
results$rankedAnova <- anova(ranked_priming_model)

describe(results$rankedAnova)

summary(aov(rankedPT ~ fading_factor + angle_factor + sound_factor))

# Kruskal Wallis Test One Way Anova by Ranks 
normalized_RTPT <- log(DATA$reactionTime_PT)
kruskal.test(normalized_RTPT~fading_factor) # where y1 is numeric and A is a factor

#	Friedman rank sum test
group_CoN <- DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_nosound), ]$reactionTime_PT
groupC_800N <- DATA[intersect(intersect(angleidx_central, fadingidx_800), soundidx_nosound), ]$reactionTime_PT 
group_C0Y <- DATA[intersect(intersect(angleidx_central, fadingidx_0), soundidx_withsound), ]$reactionTime_PT
groupP_800N <- DATA[intersect(intersect(angleidx_peripher, fadingidx_800), soundidx_nosound), ]$reactionTime_PT 
group_P0N <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_nosound), ]$reactionTime_PT 
group_P0Y <- DATA[intersect(intersect(angleidx_peripher, fadingidx_0), soundidx_withsound), ]$reactionTime_PT

friedman_input <- cbind(group_P0Y[1:280], group_P0N[1:280], groupP_800N[1:280], group_C0Y[1:280], groupC_800N[1:280], group_CoN[1:280])
friedman.test(friedman_input)


```
